---
title: "week3 assignment.NHS"
author: "hyeonsu Noh"
date: '2022-08-12'
output:
  slidy_presentation: default
  ioslides_presentation: default
---
### Introduction
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

### Review Criteria
The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## setting

```{r}
library(tidyverse)
library(plotly)
library(viridis)
```

```{r}
data(iris)
summary(iris)
```

## Interactive plot 1

```{r}
plot_ly(iris,
        type = 'scatter',
        x = ~ Sepal.Width,
        y = ~ Sepal.Length,
        color = ~ Species,
        size = 3)
```


## Interactive plot 2

```{r}
plot_ly(iris,
        type = 'scatter',
        x = ~Sepal.Width,
        y = ~Sepal.Length,
        color = ~Species,
        size = 3,
        symbol = ~Species)
```

## Interactive plot 3

```{r}
plot_ly(iris, 
        x = ~Sepal.Width, 
        y = ~Sepal.Length,
        color = ~Petal.Length,
        colors = plasma(20),
        size = ~Petal.Width,
        sizes = c(10,200))
```
